MS Keyrun Dataset Dimensions

### 2020-06-29 docs/DatasetDimensions.Rmd
fix tables update index

### Seasons:

@@

### Spatial:

Define using fishery statistical areas and match survey data as much as possible to these. Easier to map survey strata to larger fishery areas than the other way around.

@@

Responses:
```{r}
startend <- data.frame(Start = responses$StartYear,
                       End = responses$EndYear)
knitr::kable(startend)
```

**Start year rationale:**
`r knitr::kable(responses$Rationale.for.start.time, col.names = NULL)`

**End year rationale:**
`r knitr::kable(responses$Rationale.for.end.time, col.names = NULL)`

@@

**Survey season rationale:**
`r knitr::kable(responses$Rationale.for.survey.temporal.resolution, col.names = NULL)`

**Fishery season rationale:**
`r knitr::kable(responses$Rationale.for.fishery.temporal.resolution, col.names = NULL)`

@@

**Spatial rationale:**
`r knitr::kable(responses$Rationale.for.spatial.definition, col.names = NULL)`

>>>>

### Seasons: Annual fisheries, Seasonal surveys

@@

### Spatial: Fishery stat areas define Georges Bank

Define using fishery statistical areas (521-522, 525-526, 551-552, 561-562) and match survey data as much as possible to these. Easier to map survey strata to larger fishery areas than the other way around.

@@

Responses:
```{r}
startend <- data.frame(Start = responses$StartYear,
                       End = responses$EndYear)
knitr::kable(startend, booktabs=TRUE)
```

```{r} 
knitr::kable(responses$Rationale.for.start.time, col.names = "Start year rationale", booktabs=TRUE)
```

```{r}
knitr::kable(responses$Rationale.for.end.time, col.names = "End year rationale", booktabs=TRUE)
```

@@

```{r} 
knitr::kable(responses$Rationale.for.survey.temporal.resolution, col.names = "Survey season rationale", booktabs=TRUE)
```

```{r} 
knitr::kable(responses$Rationale.for.fishery.temporal.resolution, col.names = "Fishery season rationale", booktabs=TRUE)
```

@@

```{r} 
knitr::kable(responses$Rationale.for.spatial.definition, col.names = "Spatial Rationale", booktabs=TRUE)
```
